Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-05-20 doc/network.tex
tweak

Since the right-censoring effect is a sampling bias, we want to take it into account explicitly.
In contrast, spatial effects have the same effect on how the epidemic spreads as they do on observed generation intervals. 
We therefore expect that if we correct observed generation intervals for the right-censoring effect, spatial components will be taken into account implicitly. 
We can use these temporally corrected intervals to correctly link $r$ and $\RR$.
Hereafter, we will refer to the temporally corrected distribution as the ``effective'' generation-interval distribution. 
The effective distribution incorporates spatial effects. 
In a large homogeneously mixing population, and during the early phase an an epidemic, the effective distribution will be equivalent to the intrinsic distribution.

@@

To test these methods, we simulate 100 epidemics with Ebola-like parameters on an empirical network \citep{leskovec2016snap} and compare the estimates of reproductive number with empirical reproductive numbers, which we define as the average number of secondary cases generated by the first 100 infected individuals (\fref{cmp}).
\cite{trapman2016inferring} estimated the true reproductive number by dividing the total number of infected individuals in generations $2$ to $k+1$ by the total number of infected individuals in generations $1$ to $k$, where the reference generation $k$ is defined to be the first generation that contains at least 75 infected individuals;
however, individuals in later generations are potentially subject to stronger local depletion and even global depletion effects.
Therefore, we expect our empirical estimate to better reflect the infection process during the exponential growth phase.
\swp{TODO: Compare Trapman vs our estimate of empirical R0 in Appendix; Trapman estimate is much lower.}

>>>>

Since the right-censoring effect is a sampling bias, we want to take it into account explicitly.
In contrast, spatial effects have the same effect on how the epidemic spreads as they do on observed generation intervals. 
We therefore expect that if we correct observed generation intervals for the right-censoring effect, spatial components will be taken into account implicitly. 
We can use these temporally corrected intervals to correctly link $r$ and $\RR$.
Hereafter, we will refer to the temporally corrected distribution as the ``effective'' generation-interval distribution. 
The effective distribution incorporates spatial effects. 
In a large homogeneously mixing population, the effective distribution will be equivalent to the intrinsic distribution.

@@

To test these methods, we simulate 100 epidemics with Ebola-like parameters on an empirical network \citep{leskovec2016snap} and compare the estimates of reproductive number with empirical reproductive numbers, which we define as the average number of secondary cases generated by the first 100 infected individuals (\fref{cmp}).
\cite{trapman2016inferring} defined the empirical reproductive number by dividing the total number of infected individuals in generations $2$ to $k+1$ by the total number of infected individuals in generations $1$ to $k$, where the reference generation $k$ is defined to be the first generation that contains at least 75 infected individuals;
however, individuals in later generations are potentially subject to stronger local depletion and even global depletion effects.
Therefore, we expect our empirical estimate to better reflect the infection process during the exponential growth phase.
\swp{TODO: Compare Trapman vs our estimate of empirical R0 in Appendix; Trapman estimate is much lower.}
